### 2013-03-28 doc/sosp13/evaluation.tex
Edits to description of UTS.

\paragraph{Putting it all together with Unbalanced Tree Search in
    memory (UTS).}
We now show the overall performance of \Grappa running UTS.
Figure~\ref{fig:grappa-uts}. The point of this experiment is to
demonstrate whether \Grappa's context switching and communication layers can in fact
be used together, while balancing workload, to run an irregular application efficiently. 
We look at two classes of trees, T1x and T3x, from the
original benchmark. T1x trees are very shallow and wide, while T3x
trees are very deep. When the access to each vertex is a random
access, the critical path to search T3x trees is very long. On such
trees, we do not expect there to be sufficient concurrency for any
system, including \Grappa, to achieve high throughput. \TODO{plot it
    if time}. To verify this, at the 16-node data point, the average active tasks per
core over the search is 775 and 13 for T1XL and T3L, respectively.

\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_scale.pdf}
    \end{center}
    \caption{Vertices per second in UTS on \Grappa as the number of nodes grows.}
    \label{fig:grappa-uts}
\end{figure}

>>>>

\paragraph{Putting it all together with Unbalanced Tree Search in
    memory (UTS).}
We now show the overall performance of \Grappa running UTS.
Figure~\ref{fig:grappa-uts}. The point of this experiment is to
demonstrate whether \Grappa's context switching and communication layers can in fact
be used together, while balancing workload, to run an irregular application efficiently.
Visiting vertices in the distributed tree requires mostly remote accesses, and because each vertex in the tree must be visited before it can be expanded, blocking remote reads are required.
In this case, we are forced to context switch to tolerate the remote access and continue aggregating. 
We look at two classes of trees, T1x and T3x, from the
original benchmark. T1x trees are very shallow and wide, providing plentiful parallelism, while T3x
trees are very deep, causing the critical path to search T3x trees to be very long. On such
trees, we do not expect there to be sufficient concurrency for any
system, including \Grappa, to achieve high throughput. \TODO{plot it
    if time}. To verify this, at the 16-node data point, the average active tasks per
core over the search is 775 and 13 for T1XL and T3L, respectively.
% . When the access to each vertex is a random access
\begin{figure}[ht]
    \begin{center}
      \includegraphics[width=0.5\textwidth]{figs/uts_scale.pdf}
    \end{center}
    \caption{Vertices per second in UTS on \Grappa as the number of nodes grows.}
    \label{fig:grappa-uts}
\end{figure}
